---
title: "Introduction to dataSDA"
author: "Po-Wei Chen"
date: "2023-06-27"
output: 
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to dataSDA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(fig.align = 'center')
library(knitr)
library(dataSDA)
library(RSDA)
```

## Example of iGAP format Data
### Built-in Data

```{r}
data(Face.iGAP)
head(Face.iGAP)
```

### iGAP to MM

To convert iGAP files to MM format.

+ `data` = the dataframe with the iGAP format
+ `location` = the location of the symbolic variable in the data

```{r}
Face <- iGAP_to_MM(data = Face.iGAP, location = 1:6)
head(Face)
```

### RSDA format

Changes the format of the data to conform to RSDA format.

+ `data` = the conventional dataframe
+ `sym_type1` = the labels I means an interval variable, and S means set variable in location
+ `location` = the location of the sym_type in the data
+ `sym_type2` = the labels I means an interval variable, and S means set variable in var
+ `var` = the name of the symbolic variable in the data
 
```{r}
Face.tmp <- RSDA_format(data = Face, 
                        sym_type1 = c("I", "I", "I", "I", "I", "I"), 
                        location = c(1, 3, 5, 7, 9, 11))
head(Face.tmp)
```

### Clean the column names

Clean up variable names to conform to the RSDA format.

+ `data` = the conventional dataframe

```{r}
Face.clean <- clean_colnames(data = Face.tmp)
head(Face.clean)
```

### Write a symbolic data table from a CSV data file

```{r, eval = FALSE}
write_csv_table(data = Face.clean, file = 'Face_interval.csv')
```

### Read the symbolic data table and check the format

```{r}
Face.interval <- read.sym.table(file = 'Face_interval.csv', header = T, sep = ';', dec = '.', row.names = 1)
head(Face.interval)
```

### RSDA to MM

To convert RSDA format interval dataframe to MM format.

+ `data` = the RSDA format with interval dataframe
+ `RSDA` = Whether to load the RSDA package.

```{r}
Face.MM <- RSDA_to_MM(Face.interval, RSDA = TRUE)
head(Face.MM)
```

### MM to iGAP

To convert MM format interval dataframe to iGAP format.

+ `data` = the MM format with interval dataframe

```{r}
Face.iGAP_trans <- MM_to_iGAP(Face.MM)
head(Face.iGAP_trans)
```



